The mapmisc package

### 2013-11-14 pkg/mapmisc/inst/doc/mapmisc.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@626 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\usepackage[margin=1in,landscape]{geometry}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.png}

@@

<<setup,echo=FALSE,cache=FALSE,results='hide',message=FALSE>>=
library('knitr')
opts_chunk$set(echo=TRUE,message=FALSE,
		dev='png',
		fig.align='center',fig.pos='H',width=80,
		fig.height=6,fig.width=4,out.width="0.3\\textwidth"
)
par(bg="white")
library(mapmisc)
library(rgdal)
@

@@

Get a background map covering the extent of the meuse data
<<openmap,eval=FALSE>>=
nldTiles = openmap(meuse)
@
{\tt nldTiles} is a Raster with the sampe projection as {\tt meuse}
<<openmapInfo>>=
class(nldTiles)
proj4string(nldTiles)
proj4string(meuse)
@

@@

# not rotated
map.new(meuse)
plot(nldTiles, add=TRUE)
points(meuse)
scaleBar(proj4string(meuse),pos="left", bg="white")
insetMap(meuse, "topleft",map=world)

>>>>

\usepackage[margin=1in,landscape]{geometry}
\usepackage{graphicx,hyperref}
\DeclareGraphicsExtensions{.png}

@@

<<setup,echo=FALSE,cache=FALSE,results='hide',message=FALSE>>=
library('knitr')
opts_chunk$set(echo=TRUE,message=FALSE,
		dev='png',
		fig.align='center',fig.pos='H',width=80,
		fig.height=5,fig.width=3,out.width="0.3\\textwidth"
)
par(bg="white")
library(mapmisc)
library(rgdal)
@

@@

Get a background map covering the extent of the meuse data
<<openmap,eval=FALSE>>=
nldTiles = openmap(meuse)
@
{\tt nldTiles} is a Raster with the sampe projection as {\tt meuse}
<<openmapInfo>>=
class(nldTiles)
proj4string(nldTiles)
proj4string(meuse)
@
Maps which can be downloaded are shown at
\url{http://diseasemapping.r-forge.r-project.org/openmap/}

@@

# not rotated
map.new(meuse,legendRight=TRUE)
plot(nldTiles, add=TRUE)
points(meuse)
scaleBar(proj4string(meuse),pos="bottomright", bg="white")
insetMap(meuse, "topright",map=world)
